No-click browsing of large hierarchical data

### 2020-03-07 paper/HCC2020/paper.tex
...

%
% HCC用にIEEEフォーマットにしたもの
%
% 参考文献に適当なものを入れたい
%  Dynamic Queryとか no-click browsingが気持ちよい理由
%
%  https://dl.acm.org/doi/abs/10.1145/964696.964706 五十嵐氏の カスケーディングメニューのトラバース
%
% tree traverseという言葉を使いたい
%
% Dasher, LensBar
%
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

\def\up{▲}
\def\down{▼}
\def\right{▶}
\def\left{◀}

@@

\begin{abstract}
We introduce a novel simple interaction technique for finding and browsing
data in a huge hierarchical database using only two keys.
% or one rotating device.
% that can generate two different signals based on the rotation direction.

We can enjoy various kinds of movies, musics, books,
etc. distributed from many service providers like Amazon and Netflix.
However, 
finding a data from a huge database is not a trivial task. Users can
either find an entry using keywords, or using a menu based
on a hierarchical structure of the database.
After successfully finding an entry,
the user should confirm that he wants to watch it by clicking a ``select'' button.
If the user finds that the data is not the one he wanted,
he should go back to the previous state and perform the selection again.

In the past, when only a small number of ``channels'' were available
from broadcast TV stations, the only thing users could do was
using a television dial to select a ``channel'' and watch the
broadcast data.
Although the number of the sources were limited,
the user interface for selecting a station was simple.
%
We introduce a simple interaction technique called ``Gear'',
with which users can select an entry from a very large hierarchical database and
browse it instantly, just like we could select a channel and enjoy a TV program
using old television dials.
\end{abstract}

@@

The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.

@@

We can use the non-click browsing style on personal computers.
Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
} viewer to browse the contents in a folder
with simple swiping gestures (Figure \ref{coverflow}).

@@

We can also enjoy no-click browsing on a Finder.app window
when we select a file in a folder and
type arrow keys for selecting other files.
Using the ``column view'' mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).

@@

Using 4 keys might be okay on these devices, but it would be much better
if we could perform the navigation task using simpler devices that have only two keys.
In that case, we can use a rotating device like a disk or a wheel for the navigation,
since such devices can generate 2 signals based on the rotation direction.

@@

\section{Navigation method and examples}
\label{navigation}

@@

\section{Serencast: a non-click browsing service}

@@

{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki\footnote{
  \tsf{https://en.wikipedia.org/wiki/Wiki}
} system where users can share and edit texts on the web browser.
A user can create a {\SB} ``project'', and create pages
that consists of texts and links.
People can share the page and edit it interactively on their browsers
just like the Google Docs system\footnote{
  \tsf{https://www.google.com/docs/about/}
}.

@@

Since only two switches are required in the Gear interface,
any kind of input devices can be used for Gear.
We have tried various input devices and collected experiences.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  https://en.wikipedia.org/wiki/Human\_interface\_device
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  airturn pedpro
} can be used as the input device for Gear.
Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).

@@

Keys and pressure sensors can be placed anywhere:
we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

@@

After trying various devices, it became clear that simple buttons or
wheels can be put at anywhere like on the table or under a chair, and
we felt that the integration of furniture and input devices will be
important in the IoT age.

If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,

@@

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \verb+<input>+ was 4.96s.
It takes about 40\% more time than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is not a great result for Gear,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods.

We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}, and
got similar results as App2.

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, by replacing 4-way navigation to Gear.

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before,

@@

One of the authors have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.).

We can enjoy using Gear everywhere using a stick PC and a wireless mouse,
just like Amazon FireTV can be used for the same purpose.
Using {\SC} is more fun for the author, since no-click browsing is more convenient than
selection-based interface on existing systems.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}

>>>>

%
% HCC用にIEEEフォーマットにしたもの
%
% 参考文献に適当なものを入れたい
%  Dynamic Queryとか no-click browsingが気持ちよい理由
%
%  https://dl.acm.org/doi/abs/10.1145/964696.964706 五十嵐氏の カスケーディングメニューのトラバース
%
% tree traverseという言葉を使いたい
%
% Dasher, LensBar
%
% Abstractが210語あるので減らす
%
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

\def\up{\tsf{▲}}
\def\down{\tsf{▼}}
\def\right{\tsf{▶}}
\def\left{\tsf{◀}}

@@

\begin{abstract}
We introduce a novel simple interaction technique for finding and browsing
data in a huge hierarchical database using only two keys.

Finding a data from a huge hierarchical database takes time
because users should traverse the tree using a mouse or a keyboard,
and click a ``select'' button to check the content.
If the data was not appropriate,
he should go to the next entry and perform the selection task again.

In the past, when only a small number of ``channels'' were available
from broadcast TV stations, users could simply rotate
a television dial to select a channel and watch the program.
We introduce a simple interaction technique called ``Gear'',
with which users can select an entry from a large hierarchical database and
browse it instantly, just like we could select a channel and enjoy a program
using old television dials.
\end{abstract}

@@

The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a TV channel dial or a tuning dial of the radio.

@@

We can use the no-click browsing style on personal computers.
Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
} viewer to browse the contents in a folder
with simple swiping gestures (Figure \ref{coverflow}).

@@

We can also enjoy no-click browsing on the ``column view'' mode of Finder.app.
In the column view mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).
When we type an arrow key and select another file,
the contents is shown instantly without a confirm operation.

@@

Using 4 keys might be okay on these devices, but it would be better
if we could perform the navigation task using simpler devices that have only two keys.
In that case, we can use a rotating device like a disk or a wheel for the navigation,
since such devices can generate two signals based on the rotation direction.

@@

\section{Navigation method of Gear}
\label{navigation}

@@

\section{Serencast: a no-click browsing service}

@@

{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki
system where users can share and edit texts on the web browser.
A user can create a {\SB} ``project'', and create pages
that consists of texts and links.
People can share the page and edit it interactively on their browsers
just like the Google Docs system\footnote{
  \tsf{https://www.google.com/docs/about/}
}.

@@

Since only two switches are required in the Gear interface,
almost any kind of input devices can be used for Gear.
We have tried various input devices and collected experiences.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  \tsf{https://airturn.com/products/airturn-pedpro}
} can be used as an input device for Gear.
Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).

@@

@@

After trying various devices, it became clear that simple buttons or
wheels can be put at anywhere like on the table or under a chair, and
we felt that the integration of furniture and input devices will be
important in the IoT age.
%
If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,

@@

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
It takes about 40\% more time than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is a little bit disappointing,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods.

We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
got similar results as App2.

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, by replacing 4-way navigation with Gear.

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before.

@@

One of the authors have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.).

We can enjoy using Gear everywhere using a stick PC and a wireless mouse,
just like Amazon FireTV can be used for the same purpose.
Using {\SC} is more fun for the author, since no-click browsing is more comfortable than
selection-based interface on existing systems.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=84mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}
